Precise spiking motifs in neurobiological and neuromorphic data

### 2022-10-17 manuscript.tex
4.3

\subsection{Cell assemblies at multiple time scales with arbitrary lag constellations}
\subsubsection{Paper by Russo et al 2017~\citep{russo_cell_2017}}\label{paper-by-russo-et-al-2017-russo2017}
\begin{itemize}
 \item
  ``Here we present such a unifying methodological and conceptual framework which detects assembly structure at many different time scales, levels of precision, and with arbitrary internal organization.'' by~\citep{russo_cell_2017}
\item
  sliding window as in~\citep{grun_unitary_2002} (``Numerous other statistical procedures for detecting assemblies or sequential patterns have been proposed previously'') - extended to multiple lags~\citep{torre_synchronous_2016}
\item
  based on a ``non-stationarity-corrected parametric test statistic for assessing the independence of pairs'' and ``an agglomerative, heuristic clustering algorithm for fusing significant pairs into higher-order assemblies''
\end{itemize}

\subsubsection{Neural Variability and Sampling-Based Probabilistic Representations in the Visual Cortex~\citep{orban_neural_2016}}
\begin{itemize}
 \item
  Stochastic sampling links perceptual uncertainty to neural response variability
\item
  Model accounts for independent changes in strength and variability of responses
\item
  Model predicts relationship between noise, signal, and spontaneous correlations
\item
  Stimulus statistics dependence of response statistics is explained
\end{itemize}

@@

~\citep{russo_cell_2017} starts from the relatively old notion of assessing the departure of the joint spike count distribution of two units (or sets) from independence. It is based on unitary events in multiple single-neuron spiking activity~\citep{grun_unitary_2002-1} and the reliable and efficient analysis of an excess or deficiency of joint-spike events~\citep{pipa_neuroxidence_2008}. Having derived a fast, non-stationarity-corrected parametric test statistic for assessing the independence of pairs, they designed an agglomerative, heuristic clustering algorithm for fusing significant pairs into higher-order assemblies.

>>>>

\subsection{Extending the decoding at multiple time scales}

In the paper by~\citet{russo_cell_2017}, authors present a unifying methodological and conceptual framework which detects assembly structure at many different time scales, levels of precision, and with arbitrary internal organization. It uses  sliding window as in~\citep{grun_unitary_2002} and the reliable and efficient analysis of an excess or deficiency of joint-spike events~\citep{pipa_neuroxidence_2008}. They extend the measure to multiple lags~\citep{torre_synchronous_2016}. The core measure is based on a non-stationarity-corrected parametric test statistic for assessing the independence of pairs and an agglomerative, heuristic clustering algorithm for fusing significant pairs into higher-order assemblies.

% \subsubsection{Neural Variability and Sampling-Based Probabilistic Representations in the Visual Cortex~\citep{orban_neural_2016}}
% \begin{itemize}
%  \item
%   Stochastic sampling links perceptual uncertainty to neural response variability
% \item
%   Model accounts for independent changes in strength and variability of responses
% \item
%   Model predicts relationship between noise, signal, and spontaneous correlations
% \item
%   Stimulus statistics dependence of response statistics is explained
% \end{itemize}

@@
